
## element names

```{r}
c("number1"=1, "number2"=88, 295)[["number2"]]
list("John", 1, "single"=FALSE)[[1]]
```

```{r}
vec0 <- c("a", "b", "c")
vec1 <- c("number1"=1, "number2"=88, 295)
vec2 <- list("John", 1, "single"=FALSE)
```

```{r}
LETTERS
letters
```

```{r}
LETTERS[[1]]
LETTERS[[17]]
```

```{r}
names(vec1)
names(vec2)
```

  * `names()`: `names` is a function. `names()` is function call.
  
```{r}
names(vec2) <- c("name", "number of children", "single")
names(vec2)

vec2[["name"]]
```

***

```{r}
cvector <- c("a", "b", "c")
lvector <- list("a", "b", "c")
```

```{r}
cvector
lvector
```

## `$` 

  `$` is only for LIST
  
```{r}

```

```{r}
sample_data2=c(
  "對象1"=list("年齡"=54, gender="male", "north", 100), 
  "observation2"=list(age=32, "female", "south", 25), 
  "observation3"=list(28, "female", "east", NA), 
  "observation4"=list(20, "male", "east", 77)
)
```

```{r}
sample_data2 = list(
  "對象1.年齡"=54, "對象1.gender"="male", "north", 100, 32, "female", ....., 77
)
```

```{r}
sample_data2
```


```{r}
sample_data <- list(
  "對象1"=list("年齡"=54, gender="male", "north", 100), 
  "observation2"=list(age=32, "female", "south", 25), 
  "observation3"=list(28, "female", "east", NA), 
  "observation4"=c(age="20", "male", "east", "77")
)

sample_data$observation4[["age"]]

sample_data[["對象1"]]$`年齡`

sample_data$observation2$age
sample_data$observation2$age
sample_data$`對象1`$`年齡`

```


```{r}
sample_data$observation4

sample_data$"observation4"

sample_data$`observation4`

sample_data$observation4
```


  * `$` `[[]]` are for retrieving only ONE element value.
  
  * But `$` must use **element name**, not position, to retrieve. And it only works on **list**.
  

```{r}
list(
  "milk", "apple", "pork"
)
```


```{r}
list(
  "Principle of Economics",
  "Calculus",
  "Accounting"
)
```

```{r}
list(
  "Philosophy",
  "Chinese Literature"
)
```


```{r}
list(
  "Compulsory"=list(
    "Principle of Economics",
    "Calculus",
    "Accounting"
  ),
  "Selective"=list(
    "Philosophy",
    "Chinese Literature"
  )
) -> myCourses
```

  * nested list

```{r}
list("Gianandrea Noseda conducts Schumann and Mendelssohn — With Mikhail Pletnev")
```

Gianandrea Noseda conducts Schumann and Mendelssohn — With Mikhail Pletnev

  - conductor: Gianandrea Noseda
  - program composers: 
     - Schumann
     - Mendelssohn
  - pianist: Mikhail Pletnev
  
```{r}
list(
"conductor"=list("Gianandrea Noseda"),
"composers"=list("Schumann", "Mendelssohn"),
"pianist"=list("Mikhail Pletnev")
)
```

```{r}
list(
  "name"=list(
    "conductor"=list("Gianandrea Noseda"),
    "composers"=list("Schumann", "Mendelssohn"),
    "pianist"=list("Mikhail Pletnev")
    ),
  "time"=list("2021, Oct, 01"),
  "program"=list(
    "Robert Schumann, Piano Concerto in A Minor, Op. 54",
    "Felix Mendelssohn-Bartholdy, Symphony No. 4 in A Major, Op. 90, “Italian”"
  )
) -> oneConcert
```

```{r}
browseURL("https://data.gov.tw/dataset/6013")
```

https://cloud.culture.tw/frontsite/trans/SearchShowAction.do?method=doFindTypeJ&category=17

```{r}
jsonlite::fromJSON("https://cloud.culture.tw/frontsite/trans/SearchShowAction.do?method=doFindTypeJ&category=17") -> concertData
```

```{r}
# Observation by observation
concerts_obo <-
  jsonlite::fromJSON("https://cloud.culture.tw/frontsite/trans/SearchShowAction.do?method=doFindTypeJ&category=17", simplifyDataFrame = F)

# Feature by feature
concerts_fbf <-
  jsonlite::fromJSON("https://cloud.culture.tw/frontsite/trans/SearchShowAction.do?method=doFindTypeJ&category=17", simplifyDataFrame = T)
```


